---
title: "Lab 00 - Hello IDS!"
author: "Sophie Ghinculov"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Beth", "Faaiz", "Mohsin", 
           "Beatrice"),
  github_username = c("faaizm26", "bethpeters", "beashek1-spec", 
                      "mohsinabro06"), 
  colour = c("orange", "pink", 
             "orange", "brown"),
  hobby = c("running", "taekwondo", "karate", 
            "video games"),
  favourite_number = c(2, 6, 7, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot displays github_username vs favorite_number, revealing whose favorite number is what.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favorite Number",
          title = "Favorite Number 1-10")
```

The command labs() is used to modify axis, legend and plot labels. 

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

If the data frame extended to everyone taking this course, there would be a large number of x-axis variables with the majority of the y-axis correlations being 1. As a result, the data would not be very useful since most people have unique hobbies. A better way to display such data could be a pie chart. 
